
With the explosive growth of digital information over the Internet, the recommender system is considered to be one of the most effective approaches to overcome such information overload. Traditional recommendation algorithms such as item-based approaches including collaborative filtering \cite{Sarwar:2001:ICF:371920.372071,Su:2009:SCF:1592474.1722966} and matrix factorization \cite{Rendle:2010:FPM} recommend an item by learning the interaction between users and items, while content-based approaches including \cite{2011rsh..book...73L,Liu:2011,Yuan:2015} compare the auxiliary information of both user and item to recommend similar items. Further, by looking into time variant nature of recommender systems, there are time-aware recommendation approaches \cite{Gultekin_acollaborative,Tang_review:2013} that take \emph{time} as another input dimension besides item and user, which aims at explicitly modeling user interest over time slices to combine with various classic recommender algorithms. \cite{Koren:2010} develops a collaborative filtering type of approach with predictions from static average value combining with a dynamic changing factor.  \cite{Yin:2011} propose a user-tag-specific temporal interest model to track user interest over time by maximizing the time weighted data likelihood.  For better personalization, \cite{Guy:2009} propose an item-based recommender system combining with each user's social network information. Despite multiple branches of research regarding recommender system, none of these approaches take into account of hierarchical information existing in products for better structural understanding, which leaves their recommendation results sub-optimal.  

Recently, there are a group of work using Bayesian methods for recommendations. \cite{rendle2009bpr} combines the Bayesian analysis and matrix factorization together and by learning users implicit feedbacks (click \& purchase) to directly optimize the ranking results in the sense of AUC metrics. \cite{Ben-Elazar:2017} and \cite{zhang2007efficient} takes user preference consistency into account and develops a variational Bayesian personalized ranking model for better music recommendation.  However, none of these aforementioned approaches take the product rich structure into account while learning the Bayesian model, therefore the product recommendation still remains imprecise.  

In this work, our method focuses on building a generic hierarchical Bayesian learning scheme that takes account of both the user preferences and product hidden structural properties. It is able to recommend products that align to users' long term tastes. Meanwhile the learned latent variables can be well interpreted and explained, which helps us well analyze and understand users interests and preference.

%we can have better understanding on users' likes and dislikes, so to target certain group of users based on their social behavior more accurate and efficient, which is another very important topic in the advertising business.   
